Hypercoercions and a Framework for \\ Equivalence of Cast Calculi

### 2019-12-29 paper.tex
sync

To summarize, the primary contributions of this paper are:
\begin{itemize}
\item hypercoercions, a new cast representation, which
  has a structurally recursive composition and a more compact memory
  representation.
\item a framework in Agda for proving the correctness of \lazyD{} cast
  representations.
\item a formal proof that \lazyD\ hypercoercions respect the semantics
  of the \lazyD{} cast calculus.
\end{itemize}

>>>>

To summarize, the primary contributions of this paper are:
\begin{itemize}
\item hypercoercions, a new cast representation, which
  has a structurally recursive composition and a memory
  representation more compact than space-efficient coercions.
\item a framework in Agda for proving the correctness of \lazyD{} cast
  representations.
\item a formal proof that \lazyD\ hypercoercions respect the semantics
  of the \lazyD{} cast calculus.
\end{itemize}
